---
title: 'Homework #1'
output:
  html_notebook:
    number_sections: yes
  pdf_document: 
    number_sections: yes
---


# Create the following numeric vectors

* (1, 2, 3, ..., 20)

```{r}
1:20
```

* (20, 19, ..., 1)

```{r}
20:1
```

* (1, 2, 3, ..., 20, 19, 18, ..., 1)

```{r}
c(1:20,19:1)
```

* assign (7, 8, 1) to object `tmp`

```{r}
tmp <- c(7, 8, 1)
```

* (4, 6, 3, 4, 6, 3, ..., 4, 6, 3) where each element occur 10 times

```{r}
rep(c(4, 6, 4), times  = 10)
```

* (4, 6, 3, 4, 6, 3, ..., 4) where 4 occurs 11 times, 6 occurs 10 times and 3 occurs 9 times

```{r}
rep(c(4, 6, 3), times = c(11, 10, 9))
```

* create a vector $e^xcos(x)$ for vector $x=3, 3.1, 3.2, ..., 6$

```{r}
x <- seq(3, 6,.1)
data.frame(x, y = exp(x)*cos(x))
```

* $(2, \frac{2^2}{2}, \frac{2^3}{3}, ..., \frac{2^{25}}{25})$

```{r}
2^(1:25)/1:25
```

* $\sum_{i=10}^{100}(i^3 + 4i^2)$

```{r}
i <- 10:100
sum(i^3+4*i^2)
```

* $\sum_{i=1}^{25}(\frac{2^i}{i}+\frac{3^i}{i^2})$

```{r}
i <- 1:25
sum(2^i/i + 3^i/i^2)
```


Hints: `seq` and `rep` functions

# Create the follwing character and factor vectors

* create a random vector of 1000 elements containing `{0,1}`. Set seed  to 123.

```{r}
set.seed(123)
x <- sample(x = 0:1, 1000, replace = T)
head(x)
```

* based on above vector create a factor vector with levels 0 = 'No', 1 = 'Yes'

```{r}
xf <- factor(x = x, levels = 0:1, labels = c("No", "Yes"))
levels(xf)
```

* create the following character `(q1s1, q1s2, q1s3, ...., q5s1, q5s2, q5s3)`

```{r}
paste0( rep(paste0("q", 1:5, "s"), each = 3), 1:3)
```

Hints: `sample` and `paste` function


# Declare the following matrices

$$
A =
 \begin{pmatrix}
3 & 1&  -2 \\
-3 & 2 & 1 \\
-2 & 6&  3 \\
 \end{pmatrix},
$$

```{r}
A <- matrix(data = c(3, 1, -2, -3, 2, 1, -2, 6, 3), nrow = 3, byrow = T)
A
```


$$
B =
 \begin{pmatrix}
1&  2&  -2 \\
0&  2&  -1 \\
 \end{pmatrix},
$$

```{r}
B <- matrix(data = c(1, 2, -2, 0, 2, -1), ncol = 3, byrow = T) 
B
```

$$
C =
 \begin{pmatrix}
1&  2\\
3&  4\\
 \end{pmatrix}
$$

```{r}
C <- matrix(data = 1:4, ncol = 2, byrow = T)
C
```

